DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-02-25 scnn.tex
rewording of appendix C

One should not forget that a significant part of our analysis is done with a full sphere and that in practice we often use only part of the graph as the data may be incomplete (see \figref{example_maps}).
In this case, the graph setting used through this contribution correspond to assume reflective border conditions.
It is irrelevant when working on the complete sphere as this surface has no border. Nevertheless, when working with a subpart of the sphere, its border slightly affects the convolution.
As depicted in \figref{border_effects}, a filter localized near the border of a part of the sphere (via $h(\L) \b \delta_i$) no longer has an isotropic profile.
These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.
Moreover, as long as the training data comes from simulations with the same applied mask, we do not expect these effects to cause problems for the analysis.

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{border_effects}
	\caption{Convolution kernel (also called filter) $h$ localized in the center and left corner of a surface. A filter is localized on a pixel $i$ as $\T_i h = h(\L) \b \delta_i$ (see \secref{graph_convolution} and \eqnref{graph_convolution_spatial}). The graph is built from $1/12^\text{th}$ of the sphere at $N_{side} = 16$. The filter is not isotropic anymore when localized on the left corner due to border effects. The graph representation of a manifold assumes reflective border conditions.}
	\label{fig:border_effects}
\end{figure}

>>>>

The graph setting used throughout this contribution corresponds to assuming reflective border conditions.
While that is irrelevant when working on the complete sphere (as it has no border), it slightly affects the convolution operation when only a part of the sphere is considered.
As depicted in \figref{border_effects}, a filter localized near a border (via $h(\L) \b \delta_i$) is no longer isotropic.
These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.
We however do not expect these effects to cause any problem as long as the data samples cover the same area.

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{border_effects}
	\caption{Convolution kernel (also called filter) localized in the center and left corner of a graph built from $1/12^\text{th}$ of the sphere at $N_{side} = 16$.
		A filter $h$ is localized on a pixel $i$ as $\T_i h = h(\L) \b \delta_i$ (see \secref{graph_convolution}, equation~\eqnref{graph_convolution_spatial}).
	The filter is not isotropic anymore when localized on the corner as the graph representation of a manifold assumes reflective border conditions.}
	\label{fig:border_effects}
\end{figure}
